---
title: 'Base R Code #3'
author: "Mitchell Lee"
date: "10/7/2022"
output:
  pdf_document: default
  html_document: default
---
# Set Up
1. Load the tidyverse library. 
```{r}
library(tidyverse)
```

2. Load the billboard data. 
```{r}
data("billboard")
```

3. What type of data is this? (e.g. describe what's in the dataset.)
This data contains 317 songs, their artist, their date entered, and their position on the billboard top 100 throughout the weeks. 
This contains integers, dates, empty data, and characters. 


4. Print the column names from this dataset. 
```{r}
colnames(billboard)
```

5. Print the first 5 entries in the dataset. 
```{r}
head(billboard, 5)
```


# Practice
1. Create a subset of data that has Jay-Z as the only artist. How many songs are in it?
```{r}
subset(billboard, artist=="Jay-Z")
#5 songs
```


2. In the original dataset, use filter to find information about the song "All the small things." What was the highest position this song reached on the billboard 100? 
```{r}
billboard %>% filter(track=="All The Small Things")
#    It reached position 50 in week 7
```


3. Create a subset of data for songs Tim McGraw sang. Summarize the data for wk 1.
```{r}
subset(billboard, artist=="Tim McGraw")
summary(billboard$wk1, artist=="Tim McGraw")
```




